\chapter{Tropical Geometry}
\label{chp:tropical-geometry}
\epigraph{
He had bought a large map representing the sea, \\
Without the least vestige of land:\\
And the crew were much pleased when they found it to be \\
A map they could all understand. 
}{Lewis Carroll}

   Tropical geometry is an exciting new subfield of algebraic geometry
   arising, surprisingly, out of theoretical computer science. 
   Its early discoveries were made in works of \citet{Bergman1971},
   \citet{Bieri1984}. 
   The name was coined after the Hungarian-born Brazilian mathematician Imre Simon who initially wrote on this field.
   Since 1990s, algebraic geometers have found its motivations 
   and applications to classical algebraic geometry 
   (see work by \citet{Mikhalkin2006}). 
   Later through work by Sturmfels, Speyers and many others,
   tropical geometry has found its deep connections with 
   classical algebraic geometry and many other fields,
   mainly enumerative geometry, combinatorics and graph theory. 
   One exmaple of one of the main achievements of the field is the work \citet{Mikhalkin2003},
   which shows, using tropical geometry, that
   the Gromov-Witten invariants of a curve in a plane can be calculated 
   via counting the lattice paths in polygons. 
   Another example in enumerative geometry is the work by \citet{Gathmann2005}
   that hybrids combinatorics in the proofs of many enuemrative geometry identities. 
   In this manuscript, we will not dive into the details of enumerative geometry, but only show important techniques in tropical geometry, 
   in hope of motivating readers to further understand tropical geometry
   and its connection with classical geometry, combinatorics, theoretical computer science and many other fields.
   
   In this chapter, we will introduce the basic ideas in algebraic geometry
   as foundations of tropical geometry in Section 
   \ref{sec:algebraic-varieties-and-projective-varieties}. 
   Interested readers can refer to fantastic introductory textbooks
   \textit{An Invitation to Algebraic Geometry} by \citet{Smith2000}
   and \textit{Undergraduate Algebraic Geometry} by \citet{Reid1988}. 
   In Section \ref{sec:sheaves-and-schemes}, we will introduce the generalization of varieties -- schemes. 
   

    
	
	
	
	
	
	
	
	