\section{Geometric Tropicalization for $\overline{\calm_{0, w}}$}
\label{sec:geometric-tropicalization-for-m-0w}
    Moving towards our goal of discussing heavy/light Hassett spaces,
    we let $w$ be a weight vector with only heavy and light weights,
    and assume that there are at least $2$ heavy weights. 
    Such assumptions are based on Theorem II and Corollary 2.24 in \citet{Cavalieri2014}, 
    which we state as follows.
    
    \begin{theorem}[Theorem II, \citet{Cavalieri2014}]
    \label{thm:heavy-light-balanced-fan}
        The cone complex $\calm_{0, w}^{\trop}$ can be giving the structure of a balanced fan in a vector space if and only if $w$ has only heavy and light entries.
    \end{theorem}
    
    \begin{corollary}[Corollary 2.24, \citet{Cavalieri2014}]
        Let $w$ be a weight vector.
        The projection associated with $w$, $\pr_w$ contracts all top-dimensional cones of $\calm_{0, n}^{\trop}$ if and only if $w$ does not have at least two heavy entries. 
    \end{corollary}
    We want to avoid letting the projection contracts top dimensional cones
    which causes the tropical moduli space to have wrong dimension. 
    We denote the weight vector $w$ explicitly as $w = (1^k, \epsilon^l)$ such that $k + l = n$ and $\epsilon$ is light. 
    
    Applying geometric tropicalization techniques, we state the following theorem from a very recent work that describes the boundary of the compactification $\overline{\calm}_{0, w}$
    \begin{theorem}[Theorem 1.1, \citet{Ulirsch2015}]
        Let $\calm_{0, n}$ be the locus of smooth curves in $\overline{\calm}_{0, w}$.
        Then the boundary $\overline{\calm}_{0, w} \setminus \calm_{0, w}$ is a divisor with simple normal crossings. 
    \end{theorem}
    
    \begin{definition}
    \label{def:Pr}
        Let $\Pr_w$ be a projection from $T^{\binom{n}{2}}/T^n$
        by dropping all the Pl\"{u}cker coordinates $p_{ij}$ for $i \ne j$ and $w_i = w_j = \epsilon$ in the weight vector.  
    \end{definition}
    
    This projection agrees with the map that contracts the unstable rays. 
    Via the Pl\"{u}cker embedding,
    we know that the open part $\calm_{0, w}$ can be embedded into $\Pr_w(T^{\binom{n}{2}}/T^n)$. 
    The tropicalization of the map $\Pr_w$ 
    will correspondingly contract the vector $v_{ij}$ in the resultant Bergman fan, (recall that the tropicallization of $\calm_{0, n}$ gives us a fan structure). 
    
    To summarize the above remarks, 
    we have the following lemma.
    \begin{lemma}[Lemma 3.7, \citet{Cavalieri2014}]
        The geometric tropicalization of $\overline{\calm}_{0, w}$ using the Pl\"{u}cker embedding into the projectivization of the torus is identified with $\pr_w(\calm_{0, n}^{\trop})$.
    \end{lemma}
    We then state another theorem
    \begin{theorem}[Theorem 3.9, \citet{Cavalieri2014}]
    \label{thm:tropical-compactification-m-0w}
        Let $w$ be heavy/light.
        Consider the embedding
        \[
        \calm_{0, w} \hookrightarrow T_w = \Pr_w(T^{\binom{n}{2}}/T^n).
        \]
        The compactification of $\calm_{0, w}$ in $T_w$ defined by the fan $\calm_{0, w}^{\trop}$ is isomorphic to $\overline{\calm}_{0, w}$.
        The tropicalization of $\calm_{0, w}$ with respect to this embedding is $\pr_w(\calm_{0, n}^{\trop}) = \calm_{0, w}^{\trop}$.
    \end{theorem}
    
    This theorem gives us a way to find a wonderful compactification of the moduli space of heavy/light weighted stable curves inside of a toric variety defined by the tropicalization of the moduli space.
    Furthermore, the Chow ring of the compactification coincides with the Chow ring of the toric variety,
    which can be computed using the fan structure given by the tropicalization of the moduli space.
    